### 2022-05-12 manuscript.Rmd
Prettify main (within) selection models
Add OSF link

  The data and code for this study are openly available at ???.
  We have no conflict of interest to disclose.
  There were no ethical concerns since we did not collect any new data.

@@

To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false-positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993]. To this end, we adapted code from the bootstrap R package (Version `r packageVersion("bootstrap")`) [@kostyshak2019]. Specifically, we refitted the Bayesian three-level models repeatedly while leaving out a different one of the original experiments on every iteration. To take into account the variance inherent in Bayesian model estimation, we averaged over $x$ iterations of the jackknife.

@@

The data is available via (OSF link here).

@@

The code is available via (OSF link here).

>>>>

  We have no conflict of interest to disclose.
  There were no ethical concerns since we did not collect any new data.

@@

To scrutinize the robustness of the meta-analytic effect size against the influence of any individual experiment (which may or may not be a false-positive), we conducted a jackknife leave-one-out-analysis for the meta-analysis of mental rotation performance [@gee2005; @efron1993]. To this end, we adapted code from the bootstrap R package (Version `r packageVersion("bootstrap")`) [@kostyshak2019]. Specifically, we refitted the Bayesian three-level model repeatedly while leaving out a different one of the original experiments on every iteration. To take into account the variance inherent in Bayesian model estimation, we averaged over $x$ iterations of the jackknife.

We also ran trim-and-fill analyses and selection models to confirm the robustness of the results from the frequentist meta-analyses against publication bias (Supplementary Methods 2; Supplementary Tables 8 and 9) [@duval2000; @vevea1995; @vevea2005].

@@

The data for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8. Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

The code for this study is available via https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8. Note that this link is intended for peer review only and will be replaced with a public link upon acceptance.
